Examining background gene lists using simulation - comparison of different enrichment techniques

### 2024-09-11 analysis/sim/run_simpw.Rmd
fixnames

pdf("fig3_bars.pdf", width=7,height=5,pointsize=12)
par(mar=c(c(9.1, 3.5, 2.1, 1.1) ))
par(mfrow=c(1,3))
boxplot(prec,cex=0,main="precision",ylab="",col="white",las=2)
beeswarm(prec,add=TRUE,col="black",pch=19)
boxplot(rec,cex=0,main="recall",ylab="",col="white",las=2)
beeswarm(rec,add=TRUE,col="black",pch=19)
boxplot(f1,cex=0,main="F1 index",ylab="",col="white",las=2)
beeswarm(f1,add=TRUE,col="black",pch=19)
dev.off()

>>>>

pdf("fig3_box.pdf", width=7,height=5,pointsize=12)
par(mar=c(c(9.1, 3.5, 2.1, 1.1) ))
par(mfrow=c(1,3))
boxplot(prec,cex=0,main="precision",ylab="",col="white",las=2)
beeswarm(prec,add=TRUE,col="black",pch=19)
boxplot(rec,cex=0,main="recall",ylab="",col="white",las=2)
beeswarm(rec,add=TRUE,col="black",pch=19)
boxplot(f1,cex=0,main="F1 index",ylab="",col="white",las=2)
beeswarm(f1,add=TRUE,col="black",pch=19)
dev.off()
